Preprocess turk annotations

### 2020-05-06 preprocessing/human_annotations/face_hands/analysis/preprocess_turk_detections.Rmd
move human_annotations to cleaned up folder in preprocessing pipeline

# Preprocessing

```{r}
f <- dir("turk_annotations_single/")
jf <- paste("turk_annotations_single/",f,sep="")
jd <- read_csv(jf)

@@

jd$response = jd$`Answer.trial-1.label`

agreement <- jd %>%
  group_by(Input.img_src1) %>%
  summarize(agree = response[1] == response[2])
```

### Go through raw data and put in dataframe
```{r}
d.raw <- data.frame()
trial_indexes = seq(1,252,1)
files <- dir("turk_annotations/")
num_workers=20

for (f in files) {
  jf <- paste("turk_annotations/",f,sep="")
  jd <- read_csv(jf)

@@

  for (trial_ind in trial_indexes){
    trial_data = data.frame(
      ## including HITId and HITTYpe
      this_response = eval(parse(text = paste0("jd$`Answer.trial-",trial_ind,"`"))),
      full_image_path = eval(parse(text = paste0("jd$Input.img_src",trial_ind))),
      trial_number = trial_ind,
      HITID = jd$HITId,
      HITTypeId =jd$HITTypeId,
      WorkerID = jd$WorkerId
    )
    d.raw <- bind_rows(d.raw, trial_data)
  }
}

>>>>

# Preprocessing
## Not finished cleaning this up yet...
```{r}
jf <- paste0(here::here(), '/data/turk_data/raw/face_hand_detections/Batch_3858789_batch_results.csv')

jd <- read_csv(jf)

@@

jd$response = jd$`Answer.trial-1.label`
agreement <- jd %>%
  group_by(Input.img_src1) %>%
  summarize(agree = response[1] == response[2])
```

### Go through raw data and put in dataframe
```{r}
d.raw <- data.frame()
trial_indexes = seq(1,252,1)
num_workers=20
d <- read_csv(jf)

@@

for (trial_ind in trial_indexes){
    trial_data = data.frame(
      ## including HITId and HITTYpe
      this_response = eval(parse(text = paste0("jd$`Answer.trial-",trial_ind,"`"))),
      full_image_path = eval(parse(text = paste0("jd$Input.img_src",trial_ind))),
      trial_number = trial_ind,
      HITID = jd$HITId,
      HITTypeId =jd$HITTypeId,
      WorkerID = jd$WorkerId
    )
    d.raw <- bind_rows(d.raw, trial_data)
}

### 2020-05-06 preprocessing/human_annotations/face_hands/analysis/preprocess_turk_segmentations.Rmd
move human_annotations to cleaned up folder in preprocessing pipeline

```{r setup, echo = FALSE}
library(knitr)
opts_chunk$set(echo = TRUE)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(lmerTest)
library(viridis)
library(magick)
library(egg)
library(jsonlite)
theme_set(theme_few())
```

@@

```{r}
# f <- dir("turk_annotations_segmentation/")
# jf <- paste("turk_annotations_segmentation/",f,sep="")
# jd <- read_csv(jf)

f = "turk_segmentations_hands_only.csv"
jf <- paste("../../../data/",f,sep="")
jd <- read_csv(jf)

@@

# render out some of these...
# dir.create(paste0('child_face/'))
# for (i in seq(1,length(child_face_frames$full_image_path),1)){
#   image_read(as.character(child_face_frames$full_image_path[i])) %>%
#   image_append(stack = FALSE) %>%
#   image_write(file.path(paste0("child_face/", child_face_frames$short_image_path[i])))
# }

@@

### Write out csv for use in analysis
```{r}
write_csv(d,'turk_segmentations_hands_only_processed.csv')
```

```{r}
d <- d %>%
  mutate(short_image_path = str_split_fixed(full_image_path,'/',7)[,7])
```

```{r eval=FALSE}

unique_images = d$full_image_path
for (image in unique_images){
  this_image_rgb <- image_read(image)
  img <- image_draw(this_image_rgb)
  a <- d %>%
    filter(full_image_path %in% image)

>>>>

```{r setup, echo = FALSE}
library(knitr)
opts_chunk$set(echo = TRUE)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(lmerTest)
library(viridis)
library(magick)
library(jsonlite)
library(here)
library(lubridate)
theme_set(theme_few())
```

@@

```{r}
f = "turk_segmentations_hands_only.csv"
jf <- paste0(here::here(), '/data/turk_data/',f)
jd <- read_csv(jf)

@@

# render out some of these...
# dir.create(paste0('child_face/'))
for (i in seq(1,length(child_face_frames$full_image_path),1)){
  image_read(as.character(child_face_frames$full_image_path[i])) %>%
  image_append(stack = FALSE) %>%
  image_write(file.path(paste0("child_face/", child_face_frames$short_image_path[i])))
}

@@

### Write out csv for use in analysis
```{r}
write_csv(d, paste0(here::here(), '/data/turk_data/turk_segmentations_hands_only_processed', today(), '.csv'))
```

## Write out some images
```{r}
d <- d %>%
  mutate(short_image_path = str_split_fixed(full_image_path,'/',7)[,7])
```

```{r eval=FALSE}
unique_images = d$full_image_path
for (image in unique_images){
  this_image_rgb <- image_read(image)
  img <- image_draw(this_image_rgb)
  a <- d %>%
    filter(full_image_path %in% image)
